Leadership across cultures and contexts: an exploratory analysis

### 2020-04-28 leadership_across_cultures_contexts.Rmd
Changed feature names. Added female leaders to status model. Moved some plots from SI to main text.

@@

To investigate features in our data, we first removed `r num_removed` text records with no evidence for any variable.

Our qualities and functions data comprised sparse $`r nrow(all_data)` \times `r length(quality_vars)`$ and $`r nrow(all_data)` \times `r length(function_vars)`$ matrices of binary data, respectively.

Most data reduction methods did not find strong evidence of structure in the data. Here we report the cluster analysis of variables that used the correlation distance metric ($1 - cor$), and the Ward agglomeration algorithm (for results from the other methods, see the SI). Figure \@ref(fig:cluster)A displays a dendrogram from the cluster analysis of the `r length(quality_vars)` leader quality variables and Figure \@ref(fig:cluster)B displays a dendrogram from the cluster analysis of the `r length(function_vars)` leader function variables. Each cluster analysis includes two estimates of significance for how strongly each cluster within the dendrogram is supported by the data. We rely on the AU (Approximately Unbiased) *p* values, which are computed by multiscale bootstrap resampling and represented as percentages (e.g., clusters with AU values $>95$ are strongly supported, and the top-level clusters are automatically highlighted by rectangles).

@@

@@

```{r FunctionRE, fig.cap="Ethnographer and Culture random effects for function variables."}
plot_fun_auth_cult_re
```

```{r QualityRE, fig.height=8, fig.cap="Ethnographer and Culture random effects for quality variables."}
plot_qual_auth_cult_re
```

@@

```{r groupstatus, fig.cap="Estimated marginal means of a mixed effects logistic regression model of evidence for high status (0/1) as a function of group type, with random effects for ethnographer nested within culture."}
plot_emm_status_group
```

```{r statusregion, fig.cap="Estimated marginal means of a mixed effects logistic regression model of evidence for high status (0/1) as a function of subsistence strategy and region as covariates, with random effects for ethnographer nested within culture."}
plot_status_subsistence + plot_status_region + plot_layout(ncol = 1)
```

@@

p_subsis_bigman <- ggemmeans(subsis_models_sig$emmeans_subsis[[2]]) +
  feature_scale +
  labs(title = 'Big man', x = '', y = '')

p_region_bigman <- ggemmeans(subsis_models_sig$emmeans_region[[2]]) +
  feature_scale +
  labs(title = 'Big man', x = '', y = '')

>>>>

```{r groupstatus, fig.width=10, fig.cap="Estimated marginal means of a mixed effects logistic regression model of evidence for high status (0/1) as a function of group type, with random effects for ethnographer nested within culture."}
((plot_emm_status_group2 / plot_emm_status_sex2) | (plot_emm_status_subsistence2 / plot_emm_status_region2)) + plot_annotation(title = "Predictors of high status", tag_levels = 'A')
```

```{r statusregion, fig.cap="Estimated marginal means of a mixed effects logistic regression model of evidence for high status (0/1) as a function of subsistence strategy and region as covariates, with random effects for ethnographer nested within culture."}
```

@@

Our qualities and functions data comprised sparse $`r nrow(all_data)` \times `r length(quality_vars)`$ and $`r nrow(all_data)` \times `r length(function_vars)`$ matrices of binary data, respectively. Most data reduction methods did not find strong evidence of structure in the data. We therefore explored reduced matrices that removed uninformative rows with no evidence for any variable and columns with only a few text records with evidence. Stable clusters emerged with $`r nrow(df_qual)` \times `r ncol(df_qual)`$ and $`r nrow(df_func)` \times `r ncol(df_func)`$ matrices for qualities and functions, respectively.

Here we report the cluster analysis of variables that used the correlation distance metric ($1 - cor$), and the Ward agglomeration algorithm (for results from the other methods, see the SI). Figure \@ref(fig:cluster)A displays a dendrogram from the cluster analysis of the `r length(quality_vars)` leader quality variables and Figure \@ref(fig:cluster)B displays a dendrogram from the cluster analysis of the `r length(function_vars)` leader function variables. Each cluster analysis includes two estimates of significance for how strongly each cluster within the dendrogram is supported by the data. We rely on the AU (Approximately Unbiased) *p* values, which are computed by multiscale bootstrap resampling and represented as percentages (e.g., clusters with AU values $>95$ are strongly supported, and the top-level clusters are automatically highlighted by rectangles).

@@

p_subsis_bigman <- ggemmeans(subsis_models_sig$emmeans_subsis[[2]]) +
  feature_scale +
  labs(title = 'Prosocial competencies', x = '', y = '')

p_region_bigman <- ggemmeans(subsis_models_sig$emmeans_region[[2]]) +
  feature_scale +
  labs(title = 'Prosocial competencies', x = '', y = '')

@@

@@

@@

```{r FunctionRE, fig.width=10, fig.cap="Ethnographer and Culture random effects for function variables."}
plot_fun_auth_cult_re
```

```{r QualityRE, fig.width=10, fig.cap="Ethnographer and Culture random effects for quality variables."}
plot_qual_auth_cult_re
```
